### 2015-07-22 Paper_Markdown.Rmd
Added new Ladd paper to the bibliography.  Formatted a few references so thay'll work properly.

Introduction
=========================
Pollen assemblages are widely used for paleoclimatic reconstruction during the Holocene, but this method is also applied to pollen assemblages from the last Glacial period (bartlein2011pollen, kaufman2012multi), and earlier (tarasov2011progress, brewer2008climate, cheddadi1998climate).  A particular challenge for climate reconstruction using these much earlier samples is the presence of non-analogue vegetation.  Non-analogue pollen assemblages pose a problem for many reconstruction techniques, these vegetation assemblages may be the result of sets of climate variables that no longer co-exist, ecological conditions resulting from differing rates of species migration () or release from herbivores (gill2009pleistocene), or as a result of changes in human land use (Goring et al. in review?).

@@

To analyse the effects of non-analogue pollen on model skill we chose five pollen-based reconstruction methods from the literature and apply them to the modern pollen data from eastern North America.  The models are MAT, WA, WAPLS, BRT and randomForest.  Each of these models has been used previously in the pollen literature, and has strengths and weaknesses.  MAT (Overpeck, 1985) is commonly applied to reconstruct climate, for pollen, diatoms, chironomids and other taxa.  WA has a long history in the literature, and the recent development of monotone deshrinking has apparently improved performance further (Simpson, 2014?), but WA continues to suffer from a basic assumption of unimodal taxon distributions along climate gradients.

@@

```{r Fig4SampleLoss, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3, fig.width=6}
load('data/mat.res.RData')
load('data/wa.res.RData')
load('data/wapls.res.RData')
load('data/brt.res.RData')
load('data/rfor.res.RData')

@@

loss <- ggplot(data = na.samples, aes(x=distance, y=size)) + 
  geom_path(aes(group=site, color = bin), alpha = 0.4) +
  scale_color_brewer(palette = 'PiYG', type = 'div') +
  xlab('Analogue Distance') + ylab('Available Samples') +
  theme(text = element_text(size=24, family='serif'),
        axis.text = element_text(size=14, family='serif'),
        legend.position = 'none') +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand=c(0,0)) +
  geom_segment(aes(x=0.48, 
                   xend = 0.48, 
                   y = min(mat.res$sample_size, na.rm=TRUE), 
                   yend = nrow(climate)), 
               size=1, color='red', linetype=2)

@@

loss.map <-  ggplot(data = data.frame(map), aes(long, lat)) + 
  geom_polygon(aes(group=group), color='blue', alpha=0.2) +
  geom_point(data = loc.loss, 
             aes(x = long, y = lat, color = bin), alpha=0.4, size = 3) +
  theme_bw() +
  xlab('Longitude') + ylab('Latitude') +
  theme(axis.text=element_text(size=12, family='serif'),
        panel.background = element_rect(fill = 'lightblue'),
        legend.position = 'none') +
  coord_map(projection='albers', lat0=35, lat1=55, xlim=c(-100, -60), ylim=c(35, 80)) +
  scale_color_brewer(palette = 'PiYG', type = 'div')
  #scale_color_continuous(low = '#F08080', high='#4169E1')

>>>>

Introduction
=========================
Pollen assemblages are widely used for paleoclimatic reconstruction during the Holocene, but this method is also applied to pollen assemblages from the last Glacial period [@bartlein2011pollen; kaufman2012multi], and earlier [@tarasov2011progress;@brewer2008climate;@cheddadi1998climate].  A particular challenge for climate reconstruction using these much earlier samples is the presence of non-analogue vegetation.  Non-analogue pollen assemblages pose a problem for many reconstruction techniques, these vegetation assemblages may be the result of sets of climate variables that no longer co-exist, ecological conditions resulting from differing rates of species migration () or release from herbivores [@gill2009pleistocene], or as a result of changes in human land use (Goring et al. in review?).

@@

To analyse the effects of non-analogue pollen on model skill we chose five pollen-based reconstruction methods from the literature and apply them to the modern pollen data from eastern North America.  The models are MAT, WA, WAPLS, BRT and randomForest.  Each of these models has been used previously in the pollen literature, and has strengths and weaknesses.  MAT (Overpeck, 1985) is commonly applied to reconstruct climate, for pollen, diatoms, chironomids and other taxa.  WA has a long history in the literature, and the recent development of monotone deshrinking has apparently improved performance further (Simpson, 2014?), but WA continues to suffer fro a basic assumption of unimodal taxon distributions along climate gradients.

@@

```{r Fig4SampleLoss, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3, fig.width=6}

@@

loss <- ggplot(data = na.samples, aes(x=distance, y=size)) + 
  geom_path(aes(group=site, color = bin)) +
  scale_color_brewer(palette = 'PiYG', type = 'div') +
  xlab('Analogue Distance') + ylab('Available Samples') +
  theme(text = element_text(size=24, family='serif'),
        axis.text = element_text(size=14, family='serif'),
        legend.position = 'none') +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand=c(0,0)) +
  geom_segment(aes(x=0.48, 
                   xend = 0.48, 
                   y = min(mat.res$sample_size, na.rm=TRUE), 
                   yend = nrow(climate)), 
               size=1, color='red', linetype=2)

@@

loss.map <-  ggplot(data = data.frame(map), aes(long, lat)) + 
  geom_polygon(aes(group=group), color='blue', alpha=0.2) +
  geom_point(data = loc.loss, 
             aes(x = long, y = lat, color = bin), alpha=0.7, size = 3) +
  theme_bw() +
  xlab('Longitude') + ylab('Latitude') +
  theme(axis.text=element_text(size=12, family='serif'),
        panel.background = element_rect(fill = 'lightblue'),
        legend.position = 'none') +
  coord_map(projection='albers', lat0=35, lat1=55, xlim=c(-100, -60), ylim=c(35, 80)) +
  scale_color_brewer(palette = 'PiYG', type = 'div')
  #scale_color_continuous(low = '#F08080', high='#4169E1')
